---
Title: "Homework 4"
Subtitle: "Submission 1"
Author: "Alekhya Pidugu"
format:
  pdf:
    output-file: "pidugu-a-hwk4-1"
    output-ext:  "pdf"
---
# Git Repository: 

```{r results="hide", echo=FALSE, message=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)

```

```{r}
QUESTION 1

# Filter out SNPs, 800-series plans, and prescription drug only plans
filtered_data <- final.data %>%
  filter(!grepl("SNP", plan_name, ignore.case = TRUE) & 
           !(planid >= 800 & planid < 900) &
           partc_score == "Yes")

# Convert year to factor for better visualization
filtered_data$year <- as.factor(filtered_data$year)

# Create the box and whisker plot
plot <- ggplot(filtered_data, aes(x = year, y = ..count.., fill = county)) +
  geom_boxplot() +
  labs(x = "Year", y = "Plan Count", title = "Distribution of Plan Counts by County Over Time") +
  theme_minimal() +
  theme(legend.position = "none")

# Display the plot
print(plot)
```

Obviously, something is clearly wrong. I think I do not have the right variables for the Part c. But I thought it was partc_score...?

QUESTION 2
```{r results="hide", echo=FALSE, message=FALSE}
# Filter the data for the years 2010, 2012, and 2015
filtered_data <- final.data %>%
  filter(year %in% c(2010, 2012, 2015))

# Create the bar plot
bar_plot <- ggplot(filtered_data, aes(x = factor(Star_Rating), fill = factor(year))) +
  geom_bar(position = "dodge", stat = "count") +
  labs(x = "Star Rating", y = "Count", title = "Distribution of Star Ratings Over Time") +
  scale_fill_manual(values = c("2010" = "pink", "2012" = "skyblue", "2015" = "purple")) +
  theme_minimal()

# Display the plot
print(bar_plot)


